Sea-ice and macrozooplankton distribution as determinants of top predator community structure in Antarctic winter

### 2024-06-07 analysis/paper/paper.qmd
Table 4

| Variable                   | Description and units                                                                                                                                                                                                                                                                                                 | Collection location |
|:-----------------|:------------------------------------|:-----------------|
| UML depth                  | Depth at which the density differed by 0.05 kg m^−3^ from the average density of the upper 10 m of the water column [@mitchell1991] \[meters\]                                                                                                                                                                        | Station             |
| Temperature                | Average UML temperature \[°C\]                                                                                                                                                                                                                                                                                        | Station             |
| Salinity                   | Average UML salinity \[PSU\]                                                                                                                                                                                                                                                                                          | Station             |
| Chl *a*                    | Average integrated chl *a* to 100 m from bottles \[mg m^-2^\]                                                                                                                                                                                                                                                         | Station             |
| Phaeopigment               | Average integrated phaeopigment to 100 m from bottles \[mg m^-2^\]                                                                                                                                                                                                                                                    | Station             |
| Ice type                   | Factor with 4 levels: open, thin, first-year, multi-year                                                                                                                                                                                                                                                              | Transect            |
| Ice coverage               | Percent cover                                                                                                                                                                                                                                                                                                         | Transect            |
| Macrozooplankton community | Factor with 5 levels corresponding to the clusters identified by @dietrich2021winter: 1 (*Salpa* and *Clione*), 2a (small *Euphausia*, myctophid larvae, and amphipods), 2b (*Thysanoessa*), 3a (extremely diverse, including siphonophores, chaetognaths, copepods), and 3b (*E. superba* and *E. crystallorophias*) | Station             |

@@

>>>>

| Variable                   | Description and units                                                                                                                                                                                                                                                                                                 | Collection location |
|:---------|:---------------------------------------------------|:---------|
| UML depth                  | Depth at which the density differed by 0.05 kg m^−3^ from the average density of the upper 10 m of the water column [@mitchell1991] \[meters\]                                                                                                                                                                        | Station             |
| Temperature                | Average UML temperature \[°C\]                                                                                                                                                                                                                                                                                        | Station             |
| Salinity                   | Average UML salinity \[PSU\]                                                                                                                                                                                                                                                                                          | Station             |
| Chl *a*                    | Average integrated chl *a* to 100 m from bottles \[mg m^-2^\]                                                                                                                                                                                                                                                         | Station             |
| Phaeopigment               | Average integrated phaeopigment to 100 m from bottles \[mg m^-2^\]                                                                                                                                                                                                                                                    | Station             |
| Ice type                   | Factor with 4 levels: open, thin, first-year, multi-year                                                                                                                                                                                                                                                              | Transect            |
| Ice coverage               | Percent cover                                                                                                                                                                                                                                                                                                         | Transect            |
| Macrozooplankton community | Factor with 5 levels corresponding to the clusters identified by @dietrich2021winter: 1 (*Salpa* and *Clione*), 2a (small *Euphausia*, myctophid larvae, and amphipods), 2b (*Thysanoessa*), 3a (extremely diverse, including siphonophores, chaetognaths, copepods), and 3b (*E. superba* and *E. crystallorophias*) | Station             |

@@

Note: an additional header row with "No." and "Frequency" columns must be created manually to produce the formatting seen in the published paper.

```{r}
#| label: tbl-commfreq
#| tbl-cap: "Relative frequency of predator communities by year. No.: number of sites assigned to each cluster; Frequency: relative frequency of that cluster."

make_commfreqtbl(read_obj("stations_clust"))
